### 2018-09-28 README.Rmd

@@

```{r results = 'asis'}
extract_scripts_documentation("scripts", recursive = FALSE) %>% 
  mutate(
    scripts = location,
    results = map_chr(scripts, dynbenchmark::link_to_results)
  ) %>% 
  mutate(
    ix = case_when(is.na(ix) ~ "", TRUE ~ as.character(ix)),
    id = label_long(id),
    scripts = paste0("[", id, " scripts](", scripts, ")"),
    results = case_when(is.na(results) ~ "", TRUE ~ paste0("[", id, " results](", results, ")"))
  ) %>% 
  select(`\\#` = ix, id, scripts, results) %>% 
  knitr::kable()
```

@@

* [Manuscript](manuscript): Source files for producing the manuscript.
* [Package](package): An R package with several helper functions.
* [Data](data): Raw data files required by the scripts.
* [Derived](derived): Intermediate data files produced by the scripts. These files or not git committed.

@@

>>>>

(Note that this preprint is currently outdated, but cannot be updated because the paper is under revision)

@@

```{r results = 'asis'}
extract_scripts_documentation("scripts", recursive = FALSE) %>% 
  mutate(
    scripts = location,
    results = map_chr(scripts, dynbenchmark::link_to_results)
  ) %>% 
  mutate(
    ix = case_when(is.na(ix) ~ "", TRUE ~ as.character(ix)),
    id = label_long(id),
    scripts = paste0("[\U1F4C4](", scripts, ")"),
    results = case_when(is.na(results) ~ "", TRUE ~ paste0("[\U1F4CA](", results, ")"))
  ) %>% 
  select(`\\#` = ix, id, scripts, results) %>% 
  knitr::kable()
```

@@

* [Manuscript](manuscript): Source files for producing the manuscript.
* [Package](package): An R package with several helper functions.
* [Raw](raw): Files generated by hand, such as figures and spreadsheets.
* [Derived](derived): Intermediate data files produced by the scripts. These files or not git committed.

@@

## Methods

All wrapped methods are wrapped as both docker and singularity containers. These can be easily run using [*dyn*methods](https://github.com/dynverse/dynmethods).

### 2018-09-28 scripts/02-metrics/02-metric_conformity/README.Rmd

* If the position of some cells are different than in the gold standard, the score should decrease.
* If the topology of the network is different than that in the gold standard, the score should not be perfect.
* The more cells are filtered from the trajectory, the more the score should decrease.

>>>>

* If the position of some cells are different than in the reference, the score should decrease.
* If the topology of the network is different than that in the reference, the score should not be perfect.
* The more cells are filtered from the trajectory, the more the score should decrease.
